\section{Conclusions}

We have learned a lot in this project. We had heard about Node.js before, but didn't know what it did or how to use it. Throughout this project we have discovered a lot about the strengths and weaknesses of creating a web application in Node.js, and how the technology actually operates below the surface.
\\\\
Node.js lived up to its reputation of simplicity, hence our learning curve for creating the prototype has not been very steep. There were some bumps in the road, but it wouldn't take long before our issues were figured out. Things like good documentation, lots of information on the internet, a single language for both frontend and backend and the package handler contributed to the simplicity of this technology. 
\\\\
We also found that Node.js lived up to it's reputation of being powerful in many situations because of the event loop and Google's V8 engine. But this is only on a single thread, so given a problem that would require multiple threads (or thread resilience), then another technology like Java EE might be a better option.  
\\\\
After our hands-on experience of creating a web application in Node.js, we can clearly see why Node.js is one of the preferred option for creating these types of applications. Node.js popularity is also supported by the fact that JavaScript is one of, if not the most, popular programming language in the world, and it is continually growing in popularity. One aspect about JavaScript is that it also contributes to some of the drawbacks of Node.js. If qualities such as strongly typing, robustness and security is important, then Java EE would be a preferred option.
\\\\
Our experience with this technology was very good, even better than Java EE for creating this type of application. We found it to be very simple and powerful to use, even though it had it's drawbacks. We only compared it to one other technology in this report, but can come to the conclusion that Node.js would be, and often is, a very viable option compared to many other technologies for making web applications. 